\chapter*{研究業績}
\thispagestyle{fancy}


\parindent = 0pt
{\Large \bf 学術論文誌}
\begin{enumerate}[1.]
    \item Makoto Sakamoto, \underline{Takahiro Shinoda}, Takahiro Ishizu, Amane Takei and Takao Ito, ``Projection Mapping: Interactive Operation using Kinect'', International Journal of Reccent Technology and Engineering (IJRTE) ISSN: 2277-3878, Volume 8, Issue 4, pp.9307-9313, November 2019. 
\end{enumerate}
 
\vspace{10pt}

\parindent = 0pt
{\Large \bf 国際会議論文}
\begin{enumerate}[1.]
    \item Makoto Sakamoto, \underline{Takahiro Shinoda}, Takahiro Ishizu, Masamichi Hori, Amane Takei and  Takao Ito, ``A Proposal of Interactive Projection Mapping Using Kinect'', 2018 International Conference on Information and Communication Technology Robotics (ICT-ROBOT2018), IEEE, Busan, South Korea, DOI: 10.1109/ICT-ROBOT.2018.8549899, September 2018.
    \item Takahiro Ishizu, Makoto Sakamoto, Takaaki Toyota, Masamichi Hori, \underline{Takahiro Shinoda}, Amane Takei and Takao Ito, ``Hidden-Surface Processing for Interaction of Hand and Virtual Objects Using Leap Motion Controller'', 2018 International Conference on Information and Communication Technology Robotics (ICT-ROBOT2018), IEEE, Busan, South Korea, DOI: 10.1109/ICT-ROBOT.2018.8549875, September 2018.
    \item Makoto Sakamoto, Masamichi Hori, \underline{Takahiro Shinoda}, Takahiro Ishizu, Takashi Akito, Amane Takei and Takao Ito, ``A Study on Applications for Scientific Experiments Using the VR Technology'', 2018 International Conference on Information and Communication Technology Robotics (ICT-ROBOT2018), IEEE, Busan, South Korea, DOI: 10.1109/ICT-ROBOT.2018.8549868, September 2018.
    \item \underline{Takahiro Shinoda}, Makoto Sakamoto, Takahiro Ishizu,  Kenji Sakoma, Amane Takei and Takao Ito, ``Proposal of Interactive Projection Mapping using Human Detection by Machine Learning'', The 2020 International Conference on Artificial Life and Robotics(ICAROB2020), B-Con Plaza, Jan. 13-16, Beppu, Oita, Japan, 2020.
    \item Takahiro Ishizu, Makoto Sakamoto, Kenji Sakoma, \underline{Takahiro Shinoda}, Amane Takei and Takao Ito, ``Hidden Surface Removal for Interactions between User’s Bare Hands and Virtual Objects in Augmented Reality'', The 2020 International Conference on Artificial Life and Robotics(ICAROB2020), B-Con Plaza, Jan. 13-16, Beppu, Oita, Japan, 2020.
    \item Kenji Sakoma, Makoto Sakamoto, Takahiro Ishizu, \underline{Takahiro Shinoda}, Amane Takei and Takao Ito, ``Fundamental Study on Countrol of CG Character by Electroencephalography (EEG) Analysis'', The 2020 International Conference on Artificial Life and Robotics(ICAROB2020), B-Con Plaza, Jan. 13-16, Beppu, Oita, Japan, 2020.
\end{enumerate}

\vspace{10pt}

\parindent = 0pt
{\Large \bf 報告}
\begin{enumerate}[1.]
     \item 石津 貴弘，\underline{篠田 貴大}，迫間 健治，坂本 眞人，``色情報を用いた拡張現実感(AR)における隠面処理の改善''，2019年度（第72回）電気・情報関係学会九州支部連合大会，2019年9月．
     \item 迫間 健治，石津 貴弘，\underline{篠田 貴大}，坂本 眞人，``脳波解析による仮想キャラクターの動作制御の検討''，2019年度（第72回）電気・情報関係学会九州支部連合大会，2019年9月．   
\end{enumerate}